\documentclass[]{scrreprt}
\usepackage[super]{nth}
\usepackage{enumitem}
\usepackage{hyperref}
\renewcommand{\partname}{Title}
\raggedright
% Title Page
\title{Undergraduate Student Code}
\subtitle{The University of North Carolina at Chapel Hill}
\date{Updated: \today}


\begin{document}
\maketitle
\tableofcontents
\part{The Undergraduate Executive Branch}
\chapter{Composition}
\section{Undergraduate Student Body Officers}
\subsection{President of the Undergraduate Student Body (USG President)}
\emph{The President Shall:}
	\begin{enumerate}
		\item Fulfill all constitutionally mandated duties.
		\item Represent the Undergraduate Student Body, especially when working with other universities, the faculty, the administration, and campus employees.
		\item Enforce and administer all laws passed by the Undergraduate Senate
		\item Have the authority to veto bills passed by the Undergraduate Senate, provided that he/she shall exercise such veto power within seven ($7$) business days after the bill is certified and placed in the executive offices.
		\item Serve as a member of University boards and committees in accordance with the by-laws of these boards. These boards and committees include the Frank Porter Graham Union Board of Directors, General Alumni Association Board of Directors, Athletic Council, Student Television Advisory Board, the University of North Carolina Association of Student Governments, and the Chancellor's Awards Committee.
		\item Serve on the Student Fee Advisory Subcommittee.
		\item Serve as a non-voting ex officio member of all boards recognized by student government.
		\item Nominate the Undergraduate Vice-President, Treasurer, and Secretary.
		\item Nominate the chairs and members of all executive branch external appointments. Unless otherwise stated, these nominees shall automatically become executive appointees.
		\item Present the annual State of the University Address and present addresses before the Undergraduate Senate upon request.
		\item Call special elections to fill vacant elected offices, excepting special elections for Undergraduate Senate, which must be called by Undergraduate Senate with the consent of the USG President.
		\item Establish a cabinet that represents the diverse groups, needs, and interests of the Undergraduate Student Body.
		\item Appoint the Organizational Treasurer of the Undergraduate Executive Branch, Chief of Staff, Senior Advisor(s), and Director of State and External Affairs subject to a two-thirds ($\frac{2}{3}$) confirmation by the Undergraduate Senate.
		\item Present a detailed written report to the Undergraduate Senate at the first full meeting of the Undergraduate Senate after the fourteenth (\nth{14}) day of October and the last full meeting of the Undergraduate Senate in March of each year. This report should outline the issues the current administration has dealt with in the prior six months.
	\end{enumerate}
\subsubsection{Executive Orders}
The President may issue Executive Orders directing the official establishment, conduct, policies or other operations of any committee or representative that falls under the control of the Office of the Undergraduate Student Government President.
	\begin{enumerate}
		\item	Executive Orders shall be used to call special elections.
		\item	Executive Orders shall not be considered official policy of the Undergraduate Executive Branch of Student Government or the Office of the Undergraduate Student Government President until the order is signed by the USG President and certified by the USG Secretary.
		\item	The Undergraduate Student Government Secretary shall deliver a copy of each Executive Order to the University Archives, the Speaker of the Undergraduate Senate, and the respective representatives or bodies affected by each order.
		\item	Each Executive Order shall cite the provision of the Student Code under which the act is deemed to be within the power of the Office of the USG President
		\item	Each Executive Order shall be dated, numbered sequentially, and annotated for the administrative year in which the USG President was inaugurated in the following format: EO-XX-YYY, where XX represents the two-digit year in which the president was inaugurated and YYY represents the number of the executive order beginning with the number zero-zero-one ($001$) for each new administration.
		\item	Executive orders shall expire upon the swearing in of the following USG President, the issuing of another executive order that modifies or rescinds a previous order, or the date of expiration determined within an existing order.
	\end{enumerate}
\subsection{Vice-President of the Undergraduate Student Body (USG Vice-President)}
\emph{The Vice-President shall:}
	\begin{enumerate}
		\item	Fulfill all constitutionally mandated duties.
		\item	Chair the Student Advisory Committee to the Chancellor, set regular meetings, and formulate agendas in sufficient time to send copies to the Chancellor, Vice-Chancellor for Student Affairs, Executive Vice-Chancellor, and Provost.
		\item	Chair the Student Academic Advising Board, set regular meetings, and solicit student input of University issues for the discussion with the Deans of the Colleges.
		\item	Review and oversee the interview process for all executive appointments.
		\item	Deliver an updated list of all External Appointments to the Undergraduate Senate at the first meeting of the full Undergraduate Senate in both September and January.
		\item	Distribute and market the rolling application for External Appointments as needed.
		\item	Maintain electronic personal records from all External Appointments in one public archive.
	\end{enumerate}
\subsection{Treasurer of the Undergraduate Student Body (USG Treasurer)}
\emph{The Treasurer shall:}
	\begin{enumerate}
		\item	Fulfill all constitutionally mandated duties.
		\item	Execute and administer the Treasury Laws outlined in IV U.G.S.C.
		\item	Advise the Undergraduate Senate.
		\item	Serve as a non-voting, ex-officio member of the Finance Committee.
		\item	Have the supreme authority to expend any undergraduate student government funds of all organizations receiving them in accordance with V U.S.G.C.
		\item	Chair the Student Fee Audit Committee, set regular meetings, formulate agendas in sufficient time to send copies to the membership of the Committee, and present all recommendations of the committee.
		\item	Serve as a voting member on the Chancellor’s Committee on Student Fees at the chancellor’s request.
		\item	Present a financial statement every month to the Undergraduate Senate, while during regular session. This statement shall be prepared in accordance with generally accepted accounting principles and shall describe the unappropriated balance, the general surplus and changes in balances of all organizations funded by the Senate.
		\item	Submit to the Finance Committee Chair a monthly expense report documenting what stipend monies, as defined in Title V, have been spent on in the prior month.
		\item	Chair a University Sponsored Organization Task Force, made up of all External Appointments to USO, with the goal of creating a centralized dialogue regarding student fee usage.
	\end{enumerate}
\subsection{Secretary of the Undergraduate Student Body (USG Secretary)}
\emph{The Secretary shall:}
	\begin{enumerate}
		\item Coordinate outreach activities of the Undergraduate Executive Branch.
		\item Ensure that the Undergraduate Executive Branch periodically seeks direct input from the student body about the activities and policies of the Undergraduate Executive Branch.
		\item Oversee the maintenance and upkeep of the Undergraduate Executive Branch website.
		\item Certify Executive Orders.
		\item Oversee the compilation and completion of the Executive Log.
		\begin{enumerate}
			\item The Executive Log shall be defined as a collective story of the work the Undergraduate Executive Branch completed during their term. The purpose of this log is to show the campaign promises of the current administration in addition to the pitfalls and successes the administration had in completing these promises. At minimum, the Undergraduate Executive Log shall include:
			\begin{enumerate}
				\item Copies of presidential addresses
				\item Directives
				\item Statements of Policy
				\item Reports
				\item Other correspondence submitted to the USG President
				\item Memos
				\item Statistics of Impact
				\item Press Releases
				\item Campaign Posters and Program Notices (when available)
				\item Program Descriptions
				\item Any other pertinent information deemed necessary to fully explain the work accomplished.
			\end{enumerate}
		\end{enumerate}
		\item Shall ensure the completion of the Undergraduate Judicial Log by the most senior Vice Chair of the Honor Court.
		\begin{enumerate}
			\item Shall minimally include:
			\begin{enumerate}
				\item Honor System Annual Report
				\item The Undergraduate Attorney General Staff Report
				\item Any other pertinent information deemed necessary to fully explain the work accomplished.
			\end{enumerate}
		\end{enumerate}
		\item Make appropriate provisions to deposit the following materials in the university archives:
		\begin{description}
			\item[Legislation] Copies of all legislation submitted to the Undergraduate Senate for consideration together with amendments and action on such legislation, membership rosters, minutes, and other records of the Undergraduate Senate.
			\item[Records of Student Government] Copies of presidential addresses, directives, statements of policy, reports, and other correspondence submitted to the USG President, and all other correspondence and records of the Undergraduate Student Government as the Secretary shall deem of future importance or utility.
			\item[Records of the Judiciary] Copies of the records of the judicial branch of Student Government provided that this requirement shall not apply to data that would be in violation of the Family Educational Rights and Privacy Act of 1974.
			\item[The Undergraduate Student Government Annual Report] The Undergraduate Executive Log, the Undergraduate Legislative Log, the Undergraduate Judicial Log, and the Joint Governance Council Log shall be compiled in a final product called the Undergraduate Student Government Annual Report. This product will be available to the student body via digital download. Additionally, this product will be printed in four bound books to be presented at the Passing of the Book Ceremony during Spring Inauguration.
			\begin{enumerate}
				\item The Undergraduate Student Government Annual Report will be completed in pieces during the semester. A list of deadlines includes:
				\begin{enumerate}
					\item Before the First Day of Class (FDOC) at the beginning of the administration
					\item Before the end of the Fall semester when the Midyear Report will be completed
					\item Before Spring Break, so the book might be completed by inauguration
					\item Any other deadlines deemed necessary (Provided three weeks in advance)
				\end{enumerate}
				\begin{itemize}
					\item At these deadlines, each branch will prove that it has completed the parts of the Report that have already occurred. The documents will be presented to the Oversight and Advocacy Committee. The purpose of these checks is to ensure that the process is completed throughout the year and not left to the end.
					\begin{itemize}
						\item At these checks, the Oversight and Advocacy Committee will declare the portions acceptable or unacceptable.
					\end{itemize}
				\end{itemize}
				\item There will be four bound copies of the Undergraduate Student Government Annual Report, to be given to:
				\begin{enumerate}
					\item The Chancellor
					\item The Incoming SBP
					\item The Board of Trustees Chair
					\item The University Archives
				\end{enumerate}
			\end{enumerate}
		\end{description}
		\item Oversee the completion of the Undergraduate Student Government Annual Report by Spring Inauguration.
		\begin{enumerate}
			\item At each deadline during the term, if the portion is declared unacceptable, stipends for the branch officers for which the portion applies can be withheld until the portion is acceptable. In the event that extreme circumstances can be documented, that resulted in the book not being completed, the Oversight and Advocacy Committee shall have the authority to restore stipends.
			\item Following loss of stipend, if the book remains incomplete after three weeks, this shall constitute nonfeasance and shall be grounds for impeachment charges.
		\end{enumerate}
	\end{enumerate}
\subsection{Chief of Staff of the Undergraduate Executive Branch (USG Chief of Staff)}
\emph{The Chief of Staff shall:}
\begin{enumerate}
	\item	Organize recruitment drives for committee chairs and committee members.
	\item	Appoint chairs, or co-chairs, of cabinet committees, subject to the approval of the USG President.
	\item	Serve as a resource for cabinet members as they plan, organize, and execute activities.
	\item	Preside over cabinet meetings.
	\item	Establish an updated schedule (i.e. date, time, and location) of all open official meetings. That schedule shall be made public on the Undergraduate Executive Branch website.
	\item	Publish the date, time and place of any unscheduled official meetings at least twenty-four ($24$) hours in advance unless that meeting is a continuation of a previous meeting and is announced during the previous meeting.	
\end{enumerate}
\subsection{Senior Advisor(s) of the Undergraduate Executive Branch}
\emph{The Senior Advisor(s) shall:}
\begin{enumerate}
	\item	Serve as a resource for the USG President in carrying out his/her campaign platform.
	\item	Serve as a resource for cabinet members as they plan, organize, and execute activities.
	\item	Have the ability to seek their own directives outside the USG President’s platform.
\end{enumerate}
\subsection{USG Director of State and External Affairs}
\emph{The Director of State and External Affairs shall:}
\begin{enumerate}
	\item Represent the Undergraduate Executive Branch and advocate on behalf of the student body to elected local, state, and national politicians.
	\item Advise the Undergraduate Senate.
	\item Serve as a non-voting, ex-officio member of the Oversight \& Advocacy Committee.
	\item	Serve as a liaison between the Undergraduate Executive Branch and the UNC Board of Governors, the UNC-CH State Relations office, and the UNC General Administration State Relations office.
	\item	Assist in the drafting of public statements from the executive branch.
	\item	Serve as an alternate for the USG President to the UNC Association of Student Governments.
\end{enumerate}
\subsection{Organizational Treasurer of the Undergraduate Executive Branch}
\emph{The Organizational Treasurer shall:}
\begin{enumerate}
	\item Serve as a financial resource for cabinet members as they plan, organize, and execute activities.
	\item Raise funds for the Undergraduate Executive Branch from a variety of sources, including but not limited to the Undergraduate Senate and private donations.
	\item Fulfill all mandated duties of an organizational treasurer.
\end{enumerate}
\section{Cabinet}
\subsection{Cabinet Members}
\begin{itemize}
	\item Cabinet shall consist of:
	\begin{enumerate}
		\item All Executive Branch Officers.
		\item The Organizational Treasurer of the Undergraduate Executive Branch.
		\item Any roles deemed "cabinet status" by the USG President
	\end{enumerate}
	\item Members of Cabinet shall:
	\begin{enumerate}
		\item	Appoint subordinates with the approval of the USG President.
		\item	Attend all Cabinet meetings or send a subordinates in their place.
		\item	Establish whatever roles they deem necessary to achieve their goals.
		\item	Communicate regularly with a representative of the Graduate and Professional Student Government that works in a similar capacity, when necessary.
		\item	Serve on university boards and committees at the USG President’s request.
		\item	Keep detailed records of their work to facilitate the transition process.
	\end{enumerate}
\end{itemize}
\subsection{Notification of Creation of Cabinet Roles}
\emph{The USG President and/or Chief of Staff shall:}
\begin{enumerate}
	\item	Inform the Undergraduate Senate (via written document or Executive Order) of the creation of cabinet-level roles.
	\item	The notification to Senate must also include rationale as to why the cabinet position was established and the individual mandate of the role.
	\item	Sit on the Student Academic Advisory Board as one ($1$) External Appointment.
	\item	Sit on the Educational Policy Committee as one ($1$) External Appointment.
\end{enumerate}
\subsection{Training Requirement}
\begin{enumerate}
	\item All Cabinet Members shall complete the following trainings and submit proof of completion to the Chief of Staff during their term in office:
	\begin{enumerate}
		\item	One Act
		\item	Haven
		\item	Safe Zone
		\item	Racial Equity/Bias training
	\end{enumerate}
	\item	If a Cabinet Member has already completed one of these trainings, a training similar to it, or would like to attend a training similar to one of the aforementioned trainings, they may submit a request to the Chief of Staff to substitute a training or mark a training as complete.
	\item	Until a Cabinet Member has fulfilled this requirement, they shall be required to submit proof of completion for at least one of these trainings each academic semester in office, excluding the semester they were appointed.
	\item	Each term, the Executive Branch Officers will communicate with program administrators to organize one group session for Cabinet Members, the date, time, and location of which shall be sent out to Cabinet Members as close to the start of the term as is reasonably possible. Attendance will be taken at this session for the purpose of giving members of the Cabinet Members credit for attendance.
\end{enumerate}
\chapter{Succession}
\section{Presidential Succession}
\begin{enumerate}
	\item	In the event that the USG President becomes incapacitated or the office becomes vacated, the USG Vice-President shall become the Acting USG President until such time as a special election is held.
	\item	In the event that the USG Vice-President assumes the role of the USG President after the Spring General Election, a special election shall not be called and the USG Vice-President shall serve as the USG President until the next USG President is sworn in.
	\item	The order of the Succession to the Presidency shall be:
	\begin{enumerate}
		\item	USG Vice-President
		\item	Undergraduate Senate Speaker
		\item	Undergraduate Senate Speaker Pro Tempore
		\item	Undergraduate Senate Finance Committee Chair
		\item	Undergraduate Senate Rules and Judiciary Committee Chair
		\item	Undergraduate Senate Oversight and Advocacy Committee Chair
	\end{enumerate}
\end{enumerate}
\section{Executive Branch Officer Succession}
\subsection{Vacant Executive Branch Offices}
\begin{enumerate}
	\item In the event that the USG Vice-President, Secretary, Treasurer, Organizational Treasurer, Chief of Staff, Senior Advisor, or SEA Director become incapacitated, or the office becomes vacant, the USG President shall nominate a replacement within one month. The nominee must be approved by a $\frac{2}{3}$ majority vote of US.
	\item While said vacancy exists, the following procedure shall be followed:
	\begin{enumerate}
		\item	A Senior Advisor shall perform the duties of a vacant USG Vice-President.
		\item	The Finance Committee Chair shall perform the duties of a vacant USG Treasurer.
		\item	The Rules and Judiciary Committee Chair shall perform the duties of a vacant USG Secretary.
		\item The Senior Advisor, the Finance Committee Chair, and the Rules and Judiciary Chair shall continue to perform the duties of his/her respective office.
		\item	For all other positions, the nominee may act in the role provisionally until the scheduled US vote.
	\end{enumerate}
\end{enumerate}
\part{The Undergraduate Legislative Branch}
\chapter{Composition}
\section{Members of the Undergraduate Senate}
\end{document}